Transfer Learning in Visual and Relational Reasoning

### 2020-03-02 Transfer_Learning/eccv_submission/experiments_reasoning_transfer.tex
Changed font to respect constraint and trying to respect page limit.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\columnwidth]{../img/plots/cogent_reasoning_transfer.pdf}
	\caption{Accuracies of SAMNet when testing its reasoning transfer capabilities on the CoGenT-A variant.}
	\label{fig:cogent_reasoning_transfer}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\columnwidth]{../img/plots/cog_reasoning_transfer.pdf}
	\caption{Accuracies of SAMNet when testing its reasoning transfer capabilities on the Canonical variant of COG.}
	\label{fig:cog_reasoning_transfer}
\end{figure}

>>>>

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.8\columnwidth]{../img/plots/cogent_reasoning_transfer.pdf}
	\caption{Accuracies of SAMNet when testing its reasoning transfer capabilities on the CoGenT-A variant.}
	\label{fig:cogent_reasoning_transfer}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.8\columnwidth]{../img/plots/cog_reasoning_transfer.pdf}
	\caption{Accuracies of SAMNet when testing its reasoning transfer capabilities on the Canonical variant of COG.}
	\label{fig:cog_reasoning_transfer}
\end{figure}
